Vitis acerifolia LM

### 2018-12-07 V_acerifolia_LM.Rmd
acerifolia and aestivalis remove averages

We ran a LM for leaf number and total teeth.
```{r}
ac_tt_lm <- lm(avg.tt ~ leaf, data = ac_l_means)
summary(ac_tt_lm)
ac_tt_res <- resid(ac_tt_lm)
plot(avg.tt ~leaf, ac_l_means,
     ylab="Residuals", xlab="leaf",
     main="Total teeth")
```
The average leaf in the dataset has 47 teeth and the number of teeth decreases by one as leaves get older. There is a relationship between leaf number and total teeth and about half of the variance in total teeth can be explained by leaf number.

@@

We wanted to test leaf number and feret diameter ratio.
```{r}
skim(acerifolia, total.teeth)
ac_fdr_plot <- ggplot(acerifolia, aes(x = leaf, y = feret.diameter.ratio)) + geom_smooth() + theme_classic() + scale_x_continuous(breaks = seq(0, 12, 1))
ac_fdr_plot <- ac_fdr_plot +labs(x = "Leaf number",
                               y = "Feret Diameter Ratio")
ac_fdr_plot
```

@@

We ran a LM for leaf number and feret diamter ratio.
```{r}
ac_fdr_lm <- lm(avg.fdr ~ leaf, data = ac_l_means)
summary(ac_fdr_lm)
```
The average leaf in the dataset has an FDR of 0.7 and the FDR increases by ~0.009 as the leaves get older. There is a relationship between leaf number and FDR and about 75% of the variance in FDR can be explained by leaf number.

@@

```{r}
ac_fdr_seg$psi
slope(ac_fdr_seg)
ac_fdr_fitted <- fitted(ac_fdr_seg)
ac_fdr_model <- data.frame(Leaf = ac_l_means$leaf, FDR = ac_fdr_fitted)
ggplot(ac_fdr_model, aes(x = Leaf, y = FDR)) + geom_line()
ac_fdr_lines <- ac_fdr_seg$psi[, 2]
ac_fdr_mean_break <- ac_fdr_plot + geom_vline(xintercept = ac_fdr_lines, linetype = "dashed")
ac_fdr_mean_break
ggsave("ac_fdr_break.png")
```

@@

We ran a LM for leaf number and tooth area:perimeter.
```{r}
ac_tap_lm <- lm(avg.tap ~ leaf, data = ac_l_means)
summary(ac_tap_lm)
```

The average leaf in the dataset has a TAP of 0.04 and the TAP increases by 0.003 as the leaves get older. There is a relationship between leaf number and TAP and about 34% of the variance in TAP can be explained by leaf number.

@@

```{r}
ac_tap_seg$psi
slope(ac_tap_seg)
ac_tap_fitted <- fitted(ac_tap_seg)
ac_tap_model <- data.frame(Leaf = ac_l_means$leaf, TAP = ac_tap_fitted)
ggplot(ac_tap_model, aes(x = Leaf, y = TAP)) + geom_line()
ac_tap_lines <- ac_tap_seg$psi[, 2]
ac_tap_mean_break <- ac_tap_plot + geom_vline(xintercept = ac_tap_lines, linetype = "dashed")
ac_tap_mean_break
ggsave("ac_tap_break.png")
```

@@

We ran a LM for leaf number and tooth area:internal perimeter.
```{r}
ac_taip_lm <- lm(avg.taip ~ leaf, data = ac_l_means)
summary(ac_taip_lm)
```

The average leaf in the dataset has a TAIP of 0.06 and the TAIP increases by 0.003 as the leaves get older. There is not a strong relationship between leaf number and TAIP and about 22% of the variance in TAP can be explained by leaf number.

@@

```{r}
ac_taip_seg$psi
slope(ac_taip_seg)
ac_taip_fitted <- fitted(ac_taip_seg)
ac_taip_model <- data.frame(Leaf = ac_l_means$leaf, TAIP = ac_taip_fitted)
ggplot(ac_taip_model, aes(x = Leaf, y = TAIP)) + geom_line()
ac_taip_lines <- ac_taip_seg$psi[, 2]
ac_taip_mean_break <- ac_taip_plot + geom_vline(xintercept = ac_taip_lines, linetype = "dashed")
ac_taip_mean_break
ggsave("ac_taip_break.png")
```

@@

We ran a LM for leaf number and average tooth area.
```{r}
ac_ta_lm <- lm(avg.ta ~ leaf, data = ac_l_means)
summary(ac_ta_lm)
```

The average leaf in the dataset has a ATA of 0.05 and the TAIP increases by 0.007 as the leaves get older. There is a weak relationship between leaf number and ATA and about 32% of the variance in ATA can be explained by leaf number.

@@

```{r}
ac_ta_seg$psi
slope(ac_ta_seg)
ac_ta_fitted <- fitted(ac_ta_seg)
ac_ta_model <- data.frame(Leaf = ac_l_means$leaf, TA = ac_ta_fitted)
ggplot(ac_ta_model, aes(x = Leaf, y = TA)) + geom_line()
ac_ta_lines <- ac_ta_seg$psi[, 2]
ac_ta_mean_break <- ac_ta_plot + geom_vline(xintercept = ac_ta_lines, linetype = "dashed")
ac_ta_mean_break
ggsave("ac_ta_break.png")
```

@@

We ran a LM for leaf number and teeth:perimeter.
```{r}
ac_tp_lm <- lm(avg.tp ~ leaf, data = ac_l_means)
summary(ac_tp_lm)
```

The average leaf in the dataset has a TP of 1.12 and the TP decreases by 0.04 as the leaves get older. There is a relationship between leaf number and TP and about 30% of the variance in TP can be explained by leaf number.

@@

```{r}
ac_tp_seg$psi
slope(ac_tp_seg)
ac_tp_fitted <- fitted(ac_tp_seg)
ac_tp_model <- data.frame(Leaf = ac_l_means$leaf, TP = ac_tp_fitted)
ggplot(ac_tp_model, aes(x = Leaf, y = TP)) + geom_line()
ac_tp_lines <- ac_tp_seg$psi[, 2]
ac_tp_mean_break <- ac_tp_plot + geom_vline(xintercept = ac_tp_lines, linetype = "dashed")
ac_tp_mean_break
ggsave("ac_tp_break.png")
```

@@

We ran a LM for leaf number and teeth:internal perimeter.
```{r}
ac_tip_lm <- lm(avg.tip ~ leaf, data = ac_l_means)
summary(ac_tip_lm)
```

The average leaf in the dataset has a TIP of 1.67 and the TIP decreases by 0.07 as the leaves get older. There is a relationship between leaf number and TIP and about 45% of the variance in TIP can be explained by leaf number.

@@

```{r}
ac_tip_seg$psi
slope(ac_tip_seg)
ac_tip_fitted <- fitted(ac_tip_seg)
ac_tip_model <- data.frame(Leaf = ac_l_means$leaf, TIP = ac_tip_fitted)
ggplot(ac_tip_model, aes(x = Leaf, y = TIP)) + geom_line()
ac_tip_lines <- ac_tip_seg$psi[, 2]
ac_tip_mean_break <- ac_tip_plot + geom_vline(xintercept = ac_tip_lines, linetype = "dashed")
ac_tip_mean_break
ggsave("ac_tip_break.png")
```

@@

We ran a LM for leaf number and perimeter:area.
```{r}
ac_pa_lm <- lm(avg.pa ~ leaf, data = ac_l_means)
summary(ac_pa_lm)
```

The average leaf in the dataset has a PA of 2.33 and the PA decreases by 0.14 as the leaves get older. There is a relationship between leaf number and PA and about 41% of the variance in PA can be explained by leaf number.

@@

```{r}
ac_pa_seg$psi
slope(ac_pa_seg)
ac_pa_fitted <- fitted(ac_pa_seg)
ac_pa_model <- data.frame(Leaf = ac_l_means$leaf, PA = ac_pa_fitted)
ggplot(ac_pa_model, aes(x = Leaf, y = PA)) + geom_line()
ac_pa_lines <- ac_pa_seg$psi[, 2]
ac_pa_mean_break <- ac_pa_plot + geom_vline(xintercept = ac_pa_lines, linetype = "dashed")
ac_pa_mean_break
ggsave("ac_pa_break.png")
```

@@

We ran a LM for leaf number and perimeter ratio.
```{r}
ac_pr_lm <- lm(avg.pr ~ leaf, data = ac_l_means)
summary(ac_pr_lm)
```

The average leaf in the dataset has a PR of 1.5 and the PR decreases by 0.02 as the leaves get older. There is a relationship between leaf number and PR and about 68% of the variance in PR can be explained by leaf number.

@@

```{r}
ac_pr_seg$psi
slope(ac_pr_seg)
ac_pr_fitted <- fitted(ac_pr_seg)
ac_pr_model <- data.frame(Leaf = ac_l_means$leaf, PR = ac_pr_fitted)
ggplot(ac_pr_model, aes(x = Leaf, y = PR)) + geom_line()
ac_pr_lines <- ac_pr_seg$psi[, 2]
ac_pr_mean_break <- ac_pr_plot + geom_vline(xintercept = ac_pr_lines, linetype = "dashed")
ac_pr_mean_break
ggsave("ac_pr_break.png")
```

@@

We ran a LM for leaf number and compactness.
```{r}
ac_cp_lm <- lm(avg.cp ~ leaf, data = ac_l_means)
summary(ac_cp_lm)
```

The average leaf in the dataset has a CP of 92 and the CP decreases by 4.3 as the leaves get older. There is a strong relationship between leaf number and CP and about 75% of the variance in PR can be explained by leaf number.

@@

```{r}
ac_cp_seg$psi
slope(ac_cp_seg)
ac_cp_fitted <- fitted(ac_cp_seg)
ac_cp_model <- data.frame(Leaf = ac_l_means$leaf, CP = ac_cp_fitted)
ggplot(ac_cp_model, aes(x = Leaf, y = CP)) + geom_line()
ac_cp_lines <- ac_cp_seg$psi[, 2]
ac_cp_mean_break <- ac_cp_plot + geom_vline(xintercept = ac_cp_lines, linetype = "dashed")
ac_cp_mean_break
ggsave("ac_cp_break.png")
```

@@

We ran a LM for leaf number and shape factor.
```{r}
ac_sf_lm <- lm(avg.sf ~ leaf, data = ac_l_means)
summary(ac_sf_lm)
```

The average leaf in the dataset has a SF of 0.12 and the SF increases by 0.01 as the leaves get older. There is a strong relationship between leaf number and SF and about 95% of the variance in SF can be explained by leaf number.

@@

```{r}
ac_sf_seg$psi
slope(ac_sf_seg)
ac_sf_fitted <- fitted(ac_sf_seg)
ac_sf_model <- data.frame(Leaf = ac_l_means$leaf, SF = ac_sf_fitted)
ggplot(ac_sf_model, aes(x = Leaf, y = SF)) + geom_line()
ac_sf_lines <- ac_sf_seg$psi[, 2]
ac_sf_mean_break <- ac_sf_plot + geom_vline(xintercept = ac_sf_lines, linetype = "dashed")
ac_sf_mean_break
ggsave("ac_sf_break.png")
```

@@

We ran a LM for leaf number and teeth:blade area.
```{r}
ac_tba_lm <- lm(avg.tba ~ leaf, data = ac_l_means)
summary(ac_tba_lm)
```

The average leaf in the dataset has a TBA of 2.98 and the TBA decreases by 0.23 as the leaves get older. There is a strong relationship between leaf number and TBA and about 40% of the variance in TBA can be explained by leaf number.

@@

```{r}
ac_tba_seg$psi
slope(ac_tba_seg)
ac_tba_fitted <- fitted(ac_tba_seg)
ac_tba_model <- data.frame(Leaf = ac_l_means$leaf, TBA = ac_tba_fitted)
ggplot(ac_tba_model, aes(x = Leaf, y = TBA)) + geom_line()
ac_tba_lines <- ac_tba_seg$psi[, 2]
ac_tba_mean_break <- ac_tba_plot + geom_vline(xintercept = ac_tba_lines, linetype = "dashed")
ac_tba_mean_break
ggsave("ac_tba_break.png")
```

@@

We ran a LM for leaf number and tooth area:blade area in 2013.
```{r}
ac_taba13_lm <- lm(avg.taba ~ leaf, data = ac_taba13_mean)
summary(ac_taba13_lm)
```

@@

```{r}
ac_taba13_seg$psi
slope(ac_taba13_seg)
ac_taba13_fitted <- fitted(ac_taba13_seg)
ac_taba13_model <- data.frame(Leaf = ac_taba13_mean$leaf, TABA = ac_taba13_fitted)
ggplot(ac_taba13_model, aes(x = Leaf, y = TABA)) + geom_line()
ac_taba13_lines <- ac_taba13_seg$psi[, 2]
ac_taba13_mean_break <- ac_taba13_plot + geom_vline(xintercept = ac_taba13_lines, linetype = "dashed")
ac_taba13_mean_break
ggsave("ac_taba13_break.png")
```

@@

We ran a LM for leaf number and tooth area:blade area in 2015.
```{r}
ac_taba15_lm <- lm(avg.taba ~ leaf, data = ac_taba15_mean)
summary(ac_taba15_lm)
```

@@

```{r}
ac_taba15_seg$psi
slope(ac_taba15_seg)
ac_taba15_fitted <- fitted(ac_taba15_seg)
ac_taba15_model <- data.frame(Leaf = ac_taba15_mean$leaf, TABA = ac_taba15_fitted)
ggplot(ac_taba15_model, aes(x = Leaf, y = TABA)) + geom_line()
ac_taba15_lines <- ac_taba15_seg$psi[, 2]
ac_taba15_mean_break <- ac_taba15_plot + geom_vline(xintercept = ac_taba15_lines, linetype = "dashed")
ac_taba15_mean_break
ggsave("ac_taba15_break.png")
```

>>>>

We ran a LM for leaf number and total teeth.
```{r}
ac_tt_lm <- lm(total.teeth ~ leaf, data = acerifolia)
summary(ac_tt_lm)
```
The average leaf in the dataset has 48 teeth and the number of teeth decreases by 1.2 as leaves get older. There is a relationship between leaf number and total teeth and about 20% of the variance in total teeth can be explained by leaf number.

@@

We wanted to test leaf number and feret diameter ratio.
```{r}
ac_fdr_plot <- ggplot(acerifolia, aes(x = leaf, y = feret.diameter.ratio)) + geom_smooth() + theme_classic() + scale_x_continuous(breaks = seq(0, 12, 1))
ac_fdr_plot <- ac_fdr_plot +labs(x = "Leaf number",
                               y = "Feret Diameter Ratio")
ac_fdr_plot
```

@@

We ran a LM for leaf number and all feret diamter ratio.
```{r}
ac_fdr_lm <- lm(feret.diameter.ratio ~ leaf, data = acerifolia)
summary(ac_fdr_lm)
```

The average leaf in the dataset has a FDR of 0.7 and the FDR increases by 0.008 as the leaves get older. There is a relationship between leaf number and FDR and about 49% of the variance in TAP can be explained by leaf number.

@@

```{r}
ac_fdr_seg$psi
slope(ac_fdr_seg)
ac_fdr_fitted <- fitted(ac_fdr_seg)
ac_fdr_model <- data.frame(Leaf = acerifolia$leaf, FDR = ac_fdr_fitted)
ggplot(ac_fdr_model, aes(x = Leaf, y = FDR)) + geom_line()
ac_fdr_lines <- ac_fdr_seg$psi[, 2]
ac_fdr_mean_break <- ac_fdr_plot + geom_vline(xintercept = ac_fdr_lines, linetype = "dashed")
ac_fdr_mean_break
ggsave("ac_fdr_break.png")
```

@@

We ran a LM for leaf number and tooth area:perimeter.
```{r}
ac_tap_lm <- lm(tooth.area.perimeter ~ leaf, data = acerifolia)
summary(ac_tap_lm)
```

The average leaf in the dataset has a TAP of 0.04 and the TAP increases by 0.003 as the leaves get older. There is a relationship between leaf number and TAP and about 20% of the variance in TAP can be explained by leaf number.

@@

```{r}
ac_tap_seg$psi
slope(ac_tap_seg)
ac_tap_fitted <- fitted(ac_tap_seg)
ac_tap_model <- data.frame(Leaf = acerifolia$leaf, TAP = ac_tap_fitted)
ggplot(ac_tap_model, aes(x = Leaf, y = TAP)) + geom_line()
ac_tap_lines <- ac_tap_seg$psi[, 2]
ac_tap_mean_break <- ac_tap_plot + geom_vline(xintercept = ac_tap_lines, linetype = "dashed")
ac_tap_mean_break
ggsave("ac_tap_break.png")
```

@@

We ran a LM for leaf number and tooth area:internal perimeter.
```{r}
ac_taip_lm <- lm(tooth.area.int.perimeter ~ leaf, data = acerifolia)
summary(ac_taip_lm)
```

The average leaf in the dataset has a TAIP of 0.06 and the TAIP increases by 0.003 as the leaves get older. There is a strong relationship between leaf number and TAIP and about 12% of the variance in TAP can be explained by leaf number.

@@

```{r}
ac_taip_seg$psi
slope(ac_taip_seg)
ac_taip_fitted <- fitted(ac_taip_seg)
ac_taip_model <- data.frame(Leaf = acerifolia$leaf, TAIP = ac_taip_fitted)
ggplot(ac_taip_model, aes(x = Leaf, y = TAIP)) + geom_line()
ac_taip_lines <- ac_taip_seg$psi[, 2]
ac_taip_mean_break <- ac_taip_plot + geom_vline(xintercept = ac_taip_lines, linetype = "dashed")
ac_taip_mean_break
ggsave("ac_taip_break.png")
```

@@

We ran a LM for leaf number and average tooth area.
```{r}
ac_ta_lm <- lm(average.tooth.area ~ leaf, data = acerifolia)
summary(ac_ta_lm)
```

The average leaf in the dataset has a ATA of 0.05 and the TAIP increases by 0.008 as the leaves get older. There is a strong relationship between leaf number and ATA and about 18% of the variance in ATA can be explained by leaf number.

@@

```{r}
ac_ta_seg$psi
slope(ac_ta_seg)
ac_ta_fitted <- fitted(ac_ta_seg)
ac_ta_model <- data.frame(Leaf = acerifolia$leaf, TA = ac_ta_fitted)
ggplot(ac_ta_model, aes(x = Leaf, y = TA)) + geom_line()
ac_ta_lines <- ac_ta_seg$psi[, 2]
ac_ta_mean_break <- ac_ta_plot + geom_vline(xintercept = ac_ta_lines, linetype = "dashed")
ac_ta_mean_break
ggsave("ac_ta_break.png")
```

@@

We ran a LM for leaf number and teeth:perimeter.
```{r}
ac_tp_lm <- lm(teeth.perimeter ~ leaf, data = acerifolia)
summary(ac_tp_lm)
```

The average leaf in the dataset has a TP of 1.08 and the TP decreases by 0.04 as the leaves get older. There is a strong relationship between leaf number and TP and about 14% of the variance in TP can be explained by leaf number.

@@

```{r}
ac_tp_seg$psi
slope(ac_tp_seg)
ac_tp_fitted <- fitted(ac_tp_seg)
ac_tp_model <- data.frame(Leaf = acerifolia$leaf, TP = ac_tp_fitted)
ggplot(ac_tp_model, aes(x = Leaf, y = TP)) + geom_line()
ac_tp_lines <- ac_tp_seg$psi[, 2]
ac_tp_mean_break <- ac_tp_plot + geom_vline(xintercept = ac_tp_lines, linetype = "dashed")
ac_tp_mean_break
ggsave("ac_tp_break.png")
```

@@

We ran a LM for leaf number and teeth:internal perimeter.
```{r}
ac_tip_lm <- lm(teeth.int.perimeter ~ leaf, data = acerifolia)
summary(ac_tip_lm)
```

The average leaf in the dataset has a TIP of 1.67 and the TIP decreases by 0.07 as the leaves get older. There is a strong relationship between leaf number and TIP and about 22% of the variance in TIP can be explained by leaf number.

@@

```{r}
ac_tip_seg$psi
slope(ac_tip_seg)
ac_tip_fitted <- fitted(ac_tip_seg)
ac_tip_model <- data.frame(Leaf = acerifolia$leaf, TIP = ac_tip_fitted)
ggplot(ac_tip_model, aes(x = Leaf, y = TIP)) + geom_line()
ac_tip_lines <- ac_tip_seg$psi[, 2]
ac_tip_mean_break <- ac_tip_plot + geom_vline(xintercept = ac_tip_lines, linetype = "dashed")
ac_tip_mean_break
ggsave("ac_tip_break.png")
```

@@

We ran a LM for leaf number and perimeter:area.
```{r}
ac_pa_lm <- lm(perimeter.area ~ leaf, data = acerifolia)
summary(ac_pa_lm)
```

The average leaf in the dataset has a PA of 2.16 and the PA decreases by 0.13 as the leaves get older. There is a relationship between leaf number and PA and about 26% of the variance in PA can be explained by leaf number.

@@

```{r}
ac_pa_seg$psi
slope(ac_pa_seg)
ac_pa_fitted <- fitted(ac_pa_seg)
ac_pa_model <- data.frame(Leaf = acerifolia$leaf, PA = ac_pa_fitted)
ggplot(ac_pa_model, aes(x = Leaf, y = PA)) + geom_line()
ac_pa_lines <- ac_pa_seg$psi[, 2]
ac_pa_mean_break <- ac_pa_plot + geom_vline(xintercept = ac_pa_lines, linetype = "dashed")
ac_pa_mean_break
ggsave("ac_pa_break.png")
```

@@

We ran a LM for leaf number and perimeter ratio.
```{r}
ac_pr_lm <- lm(perimeter.ratio ~ leaf, data = acerifolia)
summary(ac_pr_lm)
```

The average leaf in the dataset has a PR of 1.5 and the PR decreases by 0.02 as the leaves get older. There is a relationship between leaf number and PR and about 18% of the variance in PR can be explained by leaf number.

@@

```{r}
ac_pr_seg$psi
slope(ac_pr_seg)
ac_pr_fitted <- fitted(ac_pr_seg)
ac_pr_model <- data.frame(Leaf = acerifolia$leaf, PR = ac_pr_fitted)
ggplot(ac_pr_model, aes(x = Leaf, y = PR)) + geom_line()
ac_pr_lines <- ac_pr_seg$psi[, 2]
ac_pr_mean_break <- ac_pr_plot + geom_vline(xintercept = ac_pr_lines, linetype = "dashed")
ac_pr_mean_break
ggsave("ac_pr_break.png")
```

@@

We ran a LM for leaf number and compactness.
```{r}
ac_cp_lm <- lm(compactness ~ leaf, data = acerifolia)
summary(ac_cp_lm)
```

The average leaf in the dataset has a CP of 91 and the CP decreases by 4.3 as the leaves get older. There is a strong relationship between leaf number and CP and about 47% of the variance in PR can be explained by leaf number.

@@

```{r}
ac_cp_seg$psi
slope(ac_cp_seg)
ac_cp_fitted <- fitted(ac_cp_seg)
ac_cp_model <- data.frame(Leaf = acerifolia$leaf, CP = ac_cp_fitted)
ggplot(ac_cp_model, aes(x = Leaf, y = CP)) + geom_line()
ac_cp_lines <- ac_cp_seg$psi[, 2]
ac_cp_mean_break <- ac_cp_plot + geom_vline(xintercept = ac_cp_lines, linetype = "dashed")
ac_cp_mean_break
ggsave("ac_cp_break.png")
```

@@

We ran a LM for leaf number and shape factor.
```{r}
ac_sf_lm <- lm(shape.factor ~ leaf, data = acerifolia)
summary(ac_sf_lm)
```

The average leaf in the dataset has a SF of 0.12 and the SF increases by 0.01 as the leaves get older. There is a strong relationship between leaf number and SF and about 48% of the variance in SF can be explained by leaf number.

@@

```{r}
ac_sf_seg$psi
slope(ac_sf_seg)
ac_sf_fitted <- fitted(ac_sf_seg)
ac_sf_model <- data.frame(Leaf = acerifolia$leaf, SF = ac_sf_fitted)
ggplot(ac_sf_model, aes(x = Leaf, y = SF)) + geom_line()
ac_sf_lines <- ac_sf_seg$psi[, 2]
ac_sf_mean_break <- ac_sf_plot + geom_vline(xintercept = ac_sf_lines, linetype = "dashed")
ac_sf_mean_break
ggsave("ac_sf_break.png")
```

@@

We ran a LM for leaf number and teeth:blade area.
```{r}
ac_tba_lm <- lm(teeth.blade.area ~ leaf, data = acerifolia)
summary(ac_tba_lm)
```

The average leaf in the dataset has a TBA of 2.69 and the TBA decreases by 0.21 as the leaves get older. There is a strong relationship between leaf number and TBA and about 19% of the variance in TBA can be explained by leaf number.

@@

```{r}
ac_tba_seg$psi
slope(ac_tba_seg)
ac_tba_fitted <- fitted(ac_tba_seg)
ac_tba_model <- data.frame(Leaf = acerifolia$leaf, TBA = ac_tba_fitted)
ggplot(ac_tba_model, aes(x = Leaf, y = TBA)) + geom_line()
ac_tba_lines <- ac_tba_seg$psi[, 2]
ac_tba_mean_break <- ac_tba_plot + geom_vline(xintercept = ac_tba_lines, linetype = "dashed")
ac_tba_mean_break
ggsave("ac_tba_break.png")
```

@@

We ran a LM for leaf number and tooth area:blade area in 2013.
```{r}
ac_taba13_lm <- lm(teeth.blade.area ~ leaf, data = ac_13)
summary(ac_taba13_lm)
```

@@

```{r}
ac_taba13_seg$psi
slope(ac_taba13_seg)
ac_taba13_fitted <- fitted(ac_taba13_seg)
ac_taba13_model <- data.frame(Leaf = ac_13$leaf, TABA = ac_taba13_fitted)
ggplot(ac_taba13_model, aes(x = Leaf, y = TABA)) + geom_line()
ac_taba13_lines <- ac_taba13_seg$psi[, 2]
ac_taba13_mean_break <- ac_taba13_plot + geom_vline(xintercept = ac_taba13_lines, linetype = "dashed")
ac_taba13_mean_break
ggsave("ac_taba13_break.png")
```

@@

We ran a LM for leaf number and tooth area:blade area in 2015.
```{r}
ac_taba15_lm <- lm(teeth.blade.area ~ leaf, data = ac_15)
summary(ac_taba15_lm)
```

@@

```{r}
ac_taba15_seg$psi
slope(ac_taba15_seg)
ac_taba15_fitted <- fitted(ac_taba15_seg)
ac_taba15_model <- data.frame(Leaf = ac_15$leaf, TABA = ac_taba15_fitted)
ggplot(ac_taba15_model, aes(x = Leaf, y = TABA)) + geom_line()
ac_taba15_lines <- ac_taba15_seg$psi[, 2]
ac_taba15_mean_break <- ac_taba15_plot + geom_vline(xintercept = ac_taba15_lines, linetype = "dashed")
ac_taba15_mean_break
ggsave("ac_taba15_break.png")
```
